ROBUST BAYESIAN RELIABILITY FOR COMPLEX SYSTEMS UNDER PRIOR-DATA CONFLICT

### 2017-06-04 answer-to-reviewers.tex

\emph{We are not sure if we have understood this comment well.
The survival signature allows to calculate the system reliability for arbitrary component lifetime distributions,
as is clear from Equation~(13), this is explained in detail in the cited reference (Coolen and Coolen-Maturi 2012).
We have added a sentence to emphasize this fact.}
\end{enumerate}

Furthermore, at page 15 the authors make a statement that this method has been implemented in R
and it is intended to be released as a package. Is the code already available?

\smallskip

\emph{Yes, it was our intention to provide an \textsf{R} package when we submitted the manuscript.
A package for calculating survival signatures called \texttt{ReliabilityTheory} is available,
but for other computations, we were not able to provide a package yet. %Unfortunately, the first author's ***
However, well-commented code for all computations and figures is available upon request,
and can also be found in the github repository
\texttt{http://www.github.com/geeeero/asce-asme2016}.***}

@@

\section*{Reviewer 2}

The paper is well written and interesting enough.
Nonetheless, the products of research are not really new in the fields of Bayesian analysis and reliability analysis.
In my view, there is a deep lack of bibliographical review,
and the subject is not sufficiently argued by a detailed case-study
(typically, there is no real expert information for the case-study considered, and the authors make purely subjective assumptions).
The Weibull distribution (which is in fact simplified to the Weibull one) is clearly very usual,
and the conjugate priors and virtual data are usual tools.
The authors do not detail formally what is a prior-data conflict, while several definitions exist.

\smallskip

\emph{There are several issues here:}
\begin{enumerate}
\item \emph{Contrary to the reviewer's suggestion, the work presented in this paper is novel.
First, prior-data conflict within imprecise probability has not yet been presented within a reliability context.
Secondly, the combination of imprecise probability methods that can reflect prior-data conflict with the survival signature,
enabling far more large-scale applications than without the use of the survival signature, is novel.}
\item \emph{Deep lack of bibliographic review:
there is very little work thus far on imprecise probability methods for prior-data conflict, indeed we have referred to it.
However, as is also clear from the reviewer's later comments,
the suggestion is probably to extend on literature for prior-data conflict in PRECISE Bayesian analysis.
The paper already contained a clear argument on why precise probabilistic (Bayesian) methods struggle to reflect,
and deal with, prior-data conflict, while imprecise methods, as shown, can do so in an intuitively attractive way,
namely by increasing imprecision for an event of interest.
Nevertheless, the reviewer has pointed us to some interesting papers, for which we are grateful.
We have included a brief mentioning of two of the suggested papers,
Bousquet (2008) and O'Hagan and Perrichi (2012), in the introductory section.}
\item \emph{Detail (or define?) what a prior-data conflict is:
A formal definition of prior-data conflict in the imprecise probability context is given in Definition~6
of Walter and Augustin (2009), which we cite in both the Introduction and in Section~3.
Crucially, our approach is different from precise Bayesian methods for identifying prior-data conflict (or agreement).
As we explain in Section~3,
the magnitude of the set of posteriors, as compared to the magnitude of the set of priors,
reflects the degree of prior-data conflict.
Prior-data conflict is present when imprecision increases,
and we think this is a far more attractive notion than any of the many possible definitions in precise Bayesian approaches.
We have included a short discussion about possible further research into measuring prior-data conflict
based on imprecise probabilistic inference.}
\end{enumerate}

The main advantage of this article is that it clearly presents Bayesian robustness (except the decision-theoretical part,
which is a bit prejudicial), which can be valuable for engineers.
Therefore the authors should provide, in my view, a more detailed presentation of prior-data conflicts,
provide more details about the reality of their case-study and go to the final applicability of their methodology.
A very good point is the production of a software package, but no detail is given about the name and the availability.

\emph{We do not really understand the `except' bit of the first sentence.
The main issue here is that we do NOT present a case study, and indeed make this already very clear in the text.
We mention explicitly `examples illustrating' at the end of Section~1,
and at the start of Section~6, and at the start of Section~6.1 it is clear that these are not really elicited expert opinions.
On software, please see our comment to Reviewer~1's last question.}

Here are some comments on the text:

\begin{enumerate}
\item Abstract: The term "straightforward" is to be relaxed, since prior elicitation is clearly not easy to conduct in practice.
This sentence is contradictory with l.~52, for instance.
I suspect that the authors are too optimistic since the Weibull case with a known shape parameter is very simplistic.

\smallskip
\emph{Yes, we agree that the inclusion of expert knowledege is straightforward only in the mathematical sense,
and have replaced `straightforward' in line 3 of the abstract by `possible'.}

\smallskip
\item L.~32: Could you define formally what is a ``survival signature''?

\smallskip
\emph{The survival signature is explained and defined in Section~4.2, ``System Reliability using the Survival Signature'',
more details are given in the reference Coolen and Coolen-Maturi (2012) cited in line~32 and in Section~4.2.
As mentioned in our answers to Reviewer 1's comments,
we have added a sentence to Section~4.2 highlighing the usefulness of the survival signature.}

\smallskip
\item L.~40 and following. Actually, up to a given parameterisation, all models are exponential since the shape parameters are known.
According to my experience, this situation appears scarcely.
This is the first reason why I have doubts on the reality of the motivating case-study (this motivation could besides appear within the Abtract).
The authors could have a fair description of their model by noticing it.

\smallskip
\emph{Again, our paper is not a case study.
The example is chosen to highlight the approach through a simple model, that can be widely understood.
It being simple does not mean it is not relevant!
Of course, more complicated models will be of interest for later research building on this,
in particular towards larger real world applications,
but the system failure time distribution here is already quite complex as we only make the model assumption at component level.}

\smallskip
\item P.~6: It is more traditional to use the Gamma prior for 1/lambda rather than the inverse Gamma prior on lambda.
The reason is that the virtual size $\nz$ can be in fact equal to $a$ (and not $a-1$),
since it should be possible to have $a<1$ and get a proper prior
(typically, an expert information could be considered as providing as much information as 1/2 real observation).
I am not convinced by the choice $\nz=a-1$.
Besides, a clearer interpretation of the conjugate prior (for all models allowing conjugate priors)
is the virtual data posterior prior (using an original noninformative Jeffreys prior). See [1] for details and reference therein.

\smallskip
\emph{Our parametrisation is chosen in order to facilitate the novel prior-data conflict method in the imprecise probabilistic approach.
We can allow a very small weight of the expert judgements but this would not illustrate (strong) prior data conflict well:
in order to have prior-data conflict one needs pretty informative priors.
We do not expand on the non-informative case as that is explicitly not of interest here.}

\smallskip
\item P.~7: I understand the comparison made by the authors about the prior-data conflict.
But it can be explained uniquely in terms of posterior sensitivity to a very small amount of virtual (hypothetical) or real data.
In fact, this is a bit unfair in my view to examine the prior impact alone,
then the prior and data impact through the posterior, for data which are not sampled by fixed ....as other prior guesses.
I think that the authors should read more deeply the literature dedicated to prior-data conflict
(not only the paper by Evans \& Moshonov, but others [2,3]) and summarize their conclusions:
the conflict can be detected on the sample space, or in the parameter space.
In the first solution (chosen by Evans \& Moshonov), a conflict can be not detected when the dimension increases,
because of the possible presence of ancillary statistics.
Since the authors are working only on a very simplified class of models,
for which the statistics are exhaustive, this problem remains underlying.
Furthermore, a large part of the literature is dedicated to create priors
that lead to robust conclusion in the sense a conflict is removed [4].
In [3], the symmetric notion of prior-data agreement examines the case of non-conjugate Weibull models,
and it could give ideas to the authors for improving this part of the article
(and possibly the conclusion about giving more flexibility to priors;
it seems that the virtual size $\nz$ could be a useful calibration lever, to modulate for removing a possible conflict).

\smallskip
\emph{This all comes down again to what one can do within the precise Bayesian framework,
which remains limited---the authors have certainly read the literature well (see the thesis Walter (2013), e.g.),
but the reviewer seems to miss the key point:
the imprecise framework deals fundamentally different with information and prior-data conflict,
and we claim and illustrate that this has advantages.
Note also that ``modulating $\nz$'' is not allowed in a careful (precise) Bayesian analysis:
it would make the prior dependent on the data and as such go against the fundamental principles,
although of course it is regularly done (e.g. `empirical Bayes') and it seems that researchers get away with this.
It must be emphasized that the method we present does not make the set of priors dependent on the data
and as such is fundamentally sound from the (robust) Bayesian perspective.}

\smallskip
\item P.~10 and Figure~2: It could be interesting to see (graphically) the difference between the approach of the authors
with a hierarchically Bayesian approach using uniform distributions between the bounds.
I am not sure that the difference are really high.

\smallskip
\emph{We do not think it would be that interesting to see any precise distribution in this plot, as it is all about the imprecision.}

\smallskip
\item L.~270: Place "Equations" before (19) and (20).

\smallskip
\emph{Yes, thanks, we have done so now.}

\smallskip
\item L.~293: Of which package do you talk? Other precisions from the submission?

\smallskip
\emph{Please see our comment to Reviewer~1's last question. We have changed the wording at the end of Section~4 accordingly.}

\smallskip
\item L.~342: ``One can imagine'' is a bit surprising,
since it tends to show that the considered case-study was not really examined using expert sollicitation.
Could the authors give more détails about the questioning,
or the assumptions made to admit that the results could very likely be arising from real experts?

\smallskip
\emph{As commented above, we do not present a case study here, and have expressed that very clearly before.}

\smallskip
\item Section~7: At the image of the full paper, this section is well written and interesting.
But I think that the authors should be more precise when they talk about the (more reasonable) case of two-parameter Weibull distributions.
There is a huge work on non-conjugate priors, and I think that the authors could refer to the work evoked hereinbefore,
among others, to discuss the nature of what could be a good prior for such models.

\smallskip
\emph{As we point out in Section~7, the paper should be seen as a starting point for more complex and intricate modelling and analysis,
and that further research would be needed, where the usually used discrete priors for the shape parameter would be a possible starting point.
However, a more detailed discussion on priors suitable for an imprecise probability approach is out of scope in our view,
since the requirements for an imprecise modelling approach depart markedly from those in a precise Bayesian approach.}
\end{enumerate}

### 2017-06-04 asce-paper.tex
finishing comments reviewer 2

%Invited for special issue ``The treatment of uncertainty in risk and reliability modelling and decision making''
%(special issue code SI022A), guest editors Luca Podolfillini, Bruno Sudret, Enrico Zio,
%in ASCE-ASME Journal of Risk and Uncertainty in Engineering Systems: Part A (Civil Engineering)
%
%***``For most ASCE journals, the maximum number of words and word-equivalents is 10,000 for technical papers''
%***Abstract must be 150--175 words long (this has 175), may not contain references or mathematics.
%
\begin{abstract}
In reliability engineering, data about failure events is often scarce.
To arrive at meaningful estimates for the reliability of a system,
it is therefore often necessary to also include expert information in the analysis,
which is straightforward in the Bayesian approach by using an informative prior distribution.
%
A problem called prior-data conflict then can arise:
observed data seem very surprising from the viewpoint of the prior,
i.e., information from data is in conflict with prior assumptions.
Models based on conjugate priors can be insensitive to prior-data conflict,
in the sense that the spread of the posterior distribution does not increase in case of such a conflict,
thus conveying a false sense of certainty.
%
An approach to mitigate/highlight*** this issue is presented, by considering sets of prior distributions
to model limited knowledge on Weibull distributed component lifetimes,
treating systems with arbitrary layout using the survival signature.
This approach can be seen as a robust Bayesian procedure or imprecise probability method
that reflects surprisingly early or late component failures
by wider system reliability bounds.
%We show how surprisingly early or late component failures
%result in wider system reliability bounds.
%
%and study how surprisingly early or late component failures
%affect the prediction of the reliability of a system with arbitrary layout,
%making use of survival signature to characterise the system under study.
%Our approach can be seen as a robust Bayesian procedure or imprecise probability method
%that appropriately reflects surprising data in the posterior system reliability function.
\end{abstract}
% by communicating that we can quantify the reliability of a system quite precisely when in fact we cannot.

@@

\eqref{eq:lrsysdef} and \eqref{eq:ursysdef} seem to suggest that
a full $2K$-dimensional box-constraint optimization is necessary,
but this is not the case.
Remember that $\Phi(l_1,\ldots,l_k)$ from \eqref{eq:sysrel-survsign} is non-decreasing in each of its arguments $l_1,\ldots,l_K$,
so if there is stochastic dominance in $F(l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$,
then there is, for each component type $k$,
a prior parameter pair in $\PkZ$ that minimizes system reliability, and
a prior parameter pair in $\PkZ$ that maximizes system reliability,
independently of the other component types. 
%such that system reliability is
%minimized by a distribution that gives most weight to low values of $l_k$, and
%maximized by a distribution that gives most weight to high values of $l_k$.
Indeed, stochastic dominance in $F(l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$ is provided for $\ykz$.
To see this, note that $\ykz$ gives the mean expected lifetime for type $k$ components.
Thus, higher values for $\ykz$ mean higher expected lifetimes for the components,
which in turn increases the probability that many components survive until time $t$,
and with it, decreases the propability of few or no components surviving,
so in total giving low probability weight for low values of $l_k$,
and high probability weight for high values of $l_k$. 
Therefore, for any fixed value of $\nkz$, 
the lower bound of $F(l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$ for all $l_k$ is obtained with $\ykzu$, and
the upper bound of $F(l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$ for all $l_k$ is obtained with $\ykzl$.
%
%***need formal first-order stochastic dominance in $\ykz$ result for $P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})$?
%I have it for inverse gamma posterior $f(\lambda_k\mid \nkz,\ykz, \vec{t}^k_{e_k;n_k})$,
%but not for posterior predictive***
%
There is however no corresponding result for $\nkz$,
such that different values of $\nkz$ may minimize (or maximize) $F(l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$ at different $l_k$'s.
Therefore, the $\nkz$ values for lower and upper system reliability bounds are obtained by numeric optimization.
%
\iffalse %---------------------------
\begin{linenomath*}
\begin{align} \label{eq:25}
\lefteqn{%
P(\Tsys > t\mid\{\nkz,\ykz, \mbf{t}^k_{e_k;n_k}\}_{k=1}^K)} \hspace*{10ex}\nonumber\\ 
 &= \sum_{l_1=0}^{n_1-e_1} \cdots \sum_{l_K=0}^{n_K-e_K} \Phi(l_1,\ldots,l_K) \prod_{k=1}^K
    P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})
\end{align}
\end{linenomath*}
we cannot simply plug in all the $\ul{P}(C^k_t = l_k\mid \ldots)$ %and $\ol{P}(C^k_t = l_k\mid \ldots)$
to get $\ul{P}(\Tsys > t\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k})$, % and $\ol{P}(\Tsys > t\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k})$,
as the $\ul{P}(C^k_t = l_k\mid \ldots)$ could correspond to different $(\nkz,\ykz)$ for each $l_k$.
(It would give us a lower bound for $\ul{P}(\Tsys > t\mid\ldots)$, however, but it might be very coarse.)
%
While it is clear that the lower bounds for $\ykz$ will lead to the lower system survival function,
the role of $\nkz$ is not so clear.
We therefore resort to numerical optimization of \eqref{eq:25} over $\{\nkz, k=1,\ldots,K\}$
to obtain the lower bound for $P(\Tsys > t\mid\{\nkz,\ykz, \mbf{t}^k_{e_k;n_k}\}_{k=1}^K)$.
\fi %---------------------------

@@

We have implemented the method in the statistical computing environment \textsf{R} \cite{R},
using box-constraint optimization via option \texttt{L-BFGS-B} of \texttt{optim},
and intend to release a package containing functions and code to reproduce all results and figures
for the examples in Section~\ref{sec:examples} below.

@@

The employed robust Bayesian setting provides many further modelling opportunities
beyond the explicit reaction to prior-data conflict.
These opportunities have not yet been explored and
provide a wide field for further research.
An example is our currently ongoing investigation into
extending the present model to allow also for an appropriate reflection of very strong agreement between prior and data
\cite{ipmu2016}.

***(we could add something more, e.g. that it is interesting for future research to investigate measures of prior-data conflict based on imprecise probabilistic inference or so, perhaps in the concluding remarks section, but I am not sure if that is really needed)***

>>>>

%Invited for special issue ``The treatment of uncertainty in risk and reliability modelling and decision making''
%(special issue code SI022A), guest editors Luca Podolfillini, Bruno Sudret, Enrico Zio,
%in ASCE-ASME Journal of Risk and Uncertainty in Engineering Systems: Part A (Civil Engineering)
%
%***``For most ASCE journals, the maximum number of words and word-equivalents is 10,000 for technical papers''
%***Abstract must be 150--175 words long (this has 175), may not contain references or mathematics.
%
\begin{abstract}
In reliability engineering, data about failure events is often scarce.
To arrive at meaningful estimates for the reliability of a system,
it is therefore often necessary to also include expert information in the analysis,
which is possible in the Bayesian approach by using an informative prior distribution.
%
A problem called prior-data conflict then can arise:
observed data seem very surprising from the viewpoint of the prior,
i.e., information from data is in conflict with prior assumptions.
Models based on conjugate priors can be insensitive to prior-data conflict,
in the sense that the spread of the posterior distribution does not increase in case of such a conflict,
thus conveying a false sense of certainty.
%
An approach to mitigate/highlight*** this issue is presented, by considering sets of prior distributions
to model limited knowledge on Weibull distributed component lifetimes,
treating systems with arbitrary layout using the survival signature.
This approach can be seen as a robust Bayesian procedure or imprecise probability method
that reflects surprisingly early or late component failures
by wider system reliability bounds.
%We show how surprisingly early or late component failures
%result in wider system reliability bounds.
%
%and study how surprisingly early or late component failures
%affect the prediction of the reliability of a system with arbitrary layout,
%making use of survival signature to characterise the system under study.
%Our approach can be seen as a robust Bayesian procedure or imprecise probability method
%that appropriately reflects surprising data in the posterior system reliability function.
\end{abstract}
% by communicating that we can quantify the reliability of a system quite precisely when in fact we cannot.

@@

Equations~\eqref{eq:lrsysdef} and \eqref{eq:ursysdef} seem to suggest that
a full $2K$-dimensional box-constraint optimization is necessary,
but this is not the case.
Remember that $\Phi(l_1,\ldots,l_k)$ from \eqref{eq:sysrel-survsign} is non-decreasing in each of its arguments $l_1,\ldots,l_K$,
so if there is stochastic dominance in $F(l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$,
then there is, for each component type $k$,
a prior parameter pair in $\PkZ$ that minimizes system reliability, and
a prior parameter pair in $\PkZ$ that maximizes system reliability,
independently of the other component types. 
%such that system reliability is
%minimized by a distribution that gives most weight to low values of $l_k$, and
%maximized by a distribution that gives most weight to high values of $l_k$.
Indeed, stochastic dominance in $F(l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$ is provided for $\ykz$.
To see this, note that $\ykz$ gives the mean expected lifetime for type $k$ components.
Thus, higher values for $\ykz$ mean higher expected lifetimes for the components,
which in turn increases the probability that many components survive until time $t$,
and with it, decreases the propability of few or no components surviving,
so in total giving low probability weight for low values of $l_k$,
and high probability weight for high values of $l_k$. 
Therefore, for any fixed value of $\nkz$, 
the lower bound of $F(l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$ for all $l_k$ is obtained with $\ykzu$, and
the upper bound of $F(l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$ for all $l_k$ is obtained with $\ykzl$.
%
%***need formal first-order stochastic dominance in $\ykz$ result for $P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})$?
%I have it for inverse gamma posterior $f(\lambda_k\mid \nkz,\ykz, \vec{t}^k_{e_k;n_k})$,
%but not for posterior predictive***
%
There is however no corresponding result for $\nkz$,
such that different values of $\nkz$ may minimize (or maximize) $F(l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$ at different $l_k$'s.
Therefore, the $\nkz$ values for lower and upper system reliability bounds are obtained by numeric optimization.
%
\iffalse %---------------------------
\begin{linenomath*}
\begin{align} \label{eq:25}
\lefteqn{%
P(\Tsys > t\mid\{\nkz,\ykz, \mbf{t}^k_{e_k;n_k}\}_{k=1}^K)} \hspace*{10ex}\nonumber\\ 
 &= \sum_{l_1=0}^{n_1-e_1} \cdots \sum_{l_K=0}^{n_K-e_K} \Phi(l_1,\ldots,l_K) \prod_{k=1}^K
    P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})
\end{align}
\end{linenomath*}
we cannot simply plug in all the $\ul{P}(C^k_t = l_k\mid \ldots)$ %and $\ol{P}(C^k_t = l_k\mid \ldots)$
to get $\ul{P}(\Tsys > t\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k})$, % and $\ol{P}(\Tsys > t\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k})$,
as the $\ul{P}(C^k_t = l_k\mid \ldots)$ could correspond to different $(\nkz,\ykz)$ for each $l_k$.
(It would give us a lower bound for $\ul{P}(\Tsys > t\mid\ldots)$, however, but it might be very coarse.)
%
While it is clear that the lower bounds for $\ykz$ will lead to the lower system survival function,
the role of $\nkz$ is not so clear.
We therefore resort to numerical optimization of \eqref{eq:25} over $\{\nkz, k=1,\ldots,K\}$
to obtain the lower bound for $P(\Tsys > t\mid\{\nkz,\ykz, \mbf{t}^k_{e_k;n_k}\}_{k=1}^K)$.
\fi %---------------------------

@@

We have implemented the method in the statistical computing environment \textsf{R} \cite{R},
using box-constraint optimization via option \texttt{L-BFGS-B} of \texttt{optim}.
Code for reproducing all results and figures for the examples in Section~\ref{sec:examples} below is available upon request.
%and can also be found in the github repository \texttt{http://www.github.com/geeeero/asce-asme2016}.

@@

The employed robust Bayesian setting provides many further modelling opportunities
beyond the explicit reaction to prior-data conflict.
These opportunities have not yet been explored and
provide a wide field for further research.
An example is our currently ongoing investigation into
extending the present model to allow also for an appropriate reflection of very strong agreement between prior and data
\cite{ipmu2016}.
Another interesting avenue for future research may be to
investigate measures of prior-data conflict based on imprecise probabilistic inference.
These measures could be based on changes in imprecision for certain key probabilities,
like the system reliability at a prescribed mission time.
